\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage[edges]{forest}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{TWEB}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{12}
\copyrightyear{2017}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{November 2017}
\received{Decemeber 2017}


% Document starts
\begin{document}
% Title portion. Note the short title for running heads 
\title{Career Path Predition}

\author{Jeremiah Bill}
\affiliation{%
  \institution{University of Rochester}
  \streetaddress{500 Joseph C. Wilson Blvd.}
  \city{Rocehester}
  \state{NY}
  \postcode{14627}
  \country{USA}}
\email{jbill3@u.rochester.edu}

\author{Raayan Pillai}
\affiliation{%
  \institution{University of Rochester}
  \streetaddress{500 Joseph C. Wilson Blvd.}
  \city{Rocehester}
  \state{NY}
  \postcode{14627}
  \country{USA}}
\email{rpillai3@u.rochester.edu}


  
\begin{abstract}
Multifrequency media access control has been well understood in
general wireless ad hoc networks, while in wireless sensor networks,
researchers still focus on single frequency solutions. In wireless
sensor networks, each device is typically equipped with a single
radio transceiver and applications adopt much smaller packet sizes
compared to those in general wireless ad hoc networks. Hence, the
multifrequency MAC protocols proposed for general wireless ad hoc
networks are not suitable for wireless sensor network applications,
which we further demonstrate through our simulation experiments. In
this article, we propose MMSN, which takes advantage of
multifrequency availability while, at the same time, takes into
consideration the restrictions of wireless sensor networks. Through
extensive experiments, MMSN exhibits the prominent ability to utilize
parallel transmissions among neighboring nodes. 
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010405.10010481.10010487</concept_id>
	<concept_desc>Applied computing~Forecasting</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Forecasting}



%
% End generated code
%


\keywords{Career prediction, professional analysis, neural network, decision tree, data science}




\maketitle

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{J. Bill et al.}

\input{report-body}


\end{document}
